Untwisting the Tetrahelix (v0.12)

### 2017-04-08 doc/TetrahelixUntwist.tex
typos fixed

\title{Untwisting the Tetrahelix (v0.12)}
\author{Robert L. Read \texttt{read.robert@gmail.com} \and
  Robert Gatliff \texttt{robert@toubat.org}
}

@@

We seek a formula to generate optimal tetrahelices that accepts a
parameter that allows us to design the tetrahelix conveniently.
Please refer back to Figure \ref{railanglefig}.
The pitch of the helix is an obious choice, but is not defined when the
curvature is $0$, an important special case. The radius or the axial
distance between two nodes on the same rail are obvious choices, but
perhaps the clearest choice is to build formula that takes as its
input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
formed in the X,Y plane $\angle A O B$ projecting out the $z$
axis and sighting along the positive $z$ axis. In other words, $\rho$
controls how far a rail edge of a tetrahelix deviates from being
parallel with the axis, or the ``twistiness'' of tetrahelix. We use
the parameter $\chi = 1$ to indicate a chirality or counter-clockwise,
and $\chi = -1$ for clockwise.

>>>>

\title{Untwisting the Tetrahelix (v0.12)}
\author{Robert L. Read \texttt{read.robert@gmail.com}
}

@@

We seek a formula to generate optimal tetrahelices that accepts a
parameter that allows us to design the tetrahelix conveniently.
Please refer back to Figure \ref{railanglefig}.
The pitch of the helix is an obvious choice, but is not defined when the
curvature is $0$, an important special case. The radius or the axial
distance between two nodes on the same rail are possible choices, but
perhaps the clearest choice is to build formula that takes as its
input the ``rail angle'' $\rho$. We define $\rho$ to be the angle
formed in the X,Y plane $\angle A O B$ projecting out the $z$
axis and sighting along the positive $z$ axis. In other words, $\rho$
controls how far a rail edge of a tetrahelix deviates from being
parallel with the axis, or the ``twistiness'' of tetrahelix. We use
the parameter $\chi = 1$ to indicate a chirality or counter-clockwise,
and $\chi = -1$ for clockwise.
